msprime 1.0: an efficient and extensible coalescent simulation framework

### 2021-07-09 paper.tex
Removed abctoolbox sentence, added a sentence about the all-in-one ABC softwares

\subsection*{Data interchange and interoperability}
The point of simulations is to generate data and the efficiency with
which simulated data can be incorporated into an overall application
is an important---if often overlooked---issue.
For example, Approximate Bayesian Computation
(ABC)~\citep{beaumont2002approximate,csillery2010approximate}
and more recent machine learning
methods~\citep{sheehan2016deep,schrider2018supervised,flagel2019unreasonable}
perform population genetic inference by using large numbers of
simulations as training data. Clearly, simulation efficiency is
crucial since the size and number of simulations that can be performed determines
the depth to which the model and parameter space can be sampled from.
Equally important,
however, is the efficiency with which the simulation results can be
transformed into the specific input required by the inference method.
In the case of ABC, this is usually a set of summary statistics of the sequence data.
Modern approaches such as
ABC-RF~\citep{raynal2019abc,pudlo2016abc} and
ABC-NN~\citep{csillery2012abc,blum2010abc} can accommodate large numbers of statistics
that are individually weakly informative, but jointly close to sufficient for the 
desired model or parameter.
However, the computational resources needed to calculate these statistics can be even 
greater than those used to generate the simulated datasets.
[An example would be good here? Hmmm...]

General approaches such as
ABCtoolbox~\citep{wegmann2010abctoolbox} connect to
simulation and summary statistic computation programs via text streams
and are quite flexible, but the overhead involved in processing
the text is often a computational bottleneck.
Other methods such as DIYABC~\citep{cornuet2008inferring}
or PopABC~\citep{lopes2009popabc} avoid this bottleneck by
developing their own specialised simulators, tightly integrating them
with the inference method. While this is certainly more efficient,
there is a great deal of duplication of effort and significant
room for error.

>>>>

\subsection*{Data interchange and interoperability}
The point of simulations is to generate data and the efficiency with
which simulated data can be incorporated into an overall application
is an important---if often overlooked---issue.
For example, Approximate Bayesian Computation
(ABC)~\citep{beaumont2002approximate,csillery2010approximate,wegmann2010abctoolbox}
and more recent machine learning
methods~\citep{sheehan2016deep,schrider2018supervised,flagel2019unreasonable}
perform population genetic inference by using large numbers of
simulations as training data. Clearly, simulation efficiency is
crucial since the size and number of simulations that can be performed determines
the depth to which the model and parameter space can be sampled from.
Equally important,
however, is the efficiency with which the simulation results can be
transformed into the specific input required by the inference method.
In the case of ABC, this is usually a set of summary statistics of the sequence data.
Modern approaches such as
ABC-RF~\citep{raynal2019abc,pudlo2016abc} and
ABC-NN~\citep{csillery2012abc,blum2010abc} can accommodate large numbers of user-specified statistics that are individually weakly informative,
but jointly close to sufficient for the desired model or parameter.
However, the computational resources needed to calculate these statistics can be even 
greater than those used to generate the simulated datasets.
Older software such as DIYABC~\citep{cornuet2008inferring}
or PopABC~\citep{lopes2009popabc} avoid this bottleneck by
developing their own specialised simulators, tightly integrating them
with the inference method. While this is certainly more efficient,
there is a great deal of duplication of effort and significant
room for error.
As ABC inference has become useful in an ever-widening range of applications,
these all-in-one methods risk falling behind if they do not allow users to explore
the models and statistics of most interest.
